Blum axioms and nondeterministic computation of functions

### 2015-12-15 paper.tex
paper.tex: Define the Blum axioms.

\usepackage{amsmath}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

@@

With the mathematical notion of an acceptable Gödel numbering,
we can now define the Blum axioms for complexity measures.

\begin{definition}
    Given an acceptable Gödel numbering $\phi$,
    a \emph{complexity measure} for $\phi$
    is a function $\Phi:\Sigma^* \times \Sigma^* \to \mathbb N$ of two variables
    that satisfies: \cite[p.~324]{Blum1967}
    \begin{enumerate}
        \item For every $w$ and $x$,
            $\phi_w(x)$ exists if and only if $\Phi(w, x)$ exists.
        \item For every string $w$, $x$ and every natural number $k$,
            the predicate ``$\Phi(w, x) = k$?'' is decidable.
    \end{enumerate}
\end{definition}

$\Phi(w, x)$ is the complexity of computing $\phi_w(x)$
using the program $w$.
The first axiom says that it only makes sense
to talk about the complexity of a computation that ends.
The second axiom gives minimum tools to manipulate $\Phi$ indirectly,
in the same manner we require $\phi$ to be an \emph{acceptable} Gödel numbering.
